Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-10-03 schedule.tex
start the Decision Making Support

===================================

A scheduling methodology for production services is presented
by [59]. Order decomposition into tasks, the selection of one or several
service providers to perform them, and the scheduling of the whole
manufacturing process is considered. In [60], a resource scheduling
framework is proposed. On the basis of stochastic advanced Petri net,
queue balancing cutover (QBC) strategy is put forward as a solution to
the issue of request dispatching. The scheduling of collaborative
design tasks is described in [61], presenting a new immune genetic
algorithm. Improved searching diversity based on immune strategy, but
also adaptive adjustment for probabilities of crossover and mutation
with low time complexity are achieved with this concept.

==================================

Most of the related methodologies can be archived into \textbf{four} main modules, namely \textit{Service Standardization}, \textit{Decision Making Support}, \textit{Matching Regulation} and \textit{Platform Assistance} which are going to explained in detail respectively.

@@

In order to recommand poper manufacturing service with the order user submitted, service search engine should adopt a series of well designed matching regulations. Platform will collect the hit or miss data that feeded back from user, to train the classifier.
% subsection matching_regulation (end)

>>>>

Most studies on the service scheduling issue in Cloud Manufacturing like Lartigau et al.\cite{Lartigau2012} considered the whole Cloud Manufacturing system as one giant enterprise, so that it's easy to transform the problem into the classical flexible job shop problem. However, the heteroid Users in Cloud Manufacturing always not have the consistent objects. Hence, we should take the look at personalized scheduling support in both self-oriented and platform-auxiliary scheduling. (See \autoref{sub:decision_making_support} and \ref{sub:platform_assistance} respectively)

Most of the related methodologies can be archived into \textbf{four} main modules, namely
\begin{inparaenum}[1)]
\item Service Standardization,
\item Decision Making Support,
\item Matching Regulation and
\item Platform Assistance,
\end{inparaenum} which are going to be explained in detail respectively.

@@

In order to recommand poper manufacturing service with the order user submitted, Cloud Manufacturing platfrom should provide best-match solution, thus service search engine need to adopt a series of well designed matching regulations. Platform will collect the hit or miss data that feeded back from user, to train the classifier.
% subsection matching_regulation (end)
